---
title: "ESM 244 - Lab 8"
author: "Margaux Sleckman"
date: "March 8, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


###Load the packages
```{r}

library(tidyverse)
library(sf)
library(spatstat)
library(leaflet)
library(maptools)
library(sp)
library(tmap)

```

###Colomn graph of Texas Oil Spills 
```{r}

oil_spills <-read_csv("oil_spills.csv")

df<- oil_spills %>% 
  filter(`Accident State`=="TX" & `Accident Year`<2017) %>% 
  group_by(`Accident Year`) %>% 
  summarise(Loss = sum(`Net Loss (Barrels)`))

colnames(df) <-c("Year","Loss")

ggplot(df, aes(x=Year, y=Loss))+
  geom_col()
         

```

### Leaflet plot of spill locations in TX in 2016

```{r}

df_loc <- oil_spills %>% 
  filter(`Accident State`=="TX" & `Accident Year`=="2016") %>% 
  select(Latitude, Longitude, `Net Loss (Barrels)`)
colnames(df_loc)<-c("latitude","longitude","net_loss")

oil_sf<- st_as_sf(df_loc, coords = c("longitude","latitude"), crs = 4326)

leaflet(oil_sf) %>% 
  addTiles()%>%
  addMarkers()
```



## tmap plot with the texas state shapefile
```{r }

states <-st_read(dsn=".", layer="states")

tex_border <-states %>% 
  filter(STATE_NAME == "Texas") %>% 
  st_transform(4326)

plot(tex_border)

tm_shape(tex_border)+
  tm_polygons()+
  tm_shape(oil_sf)+
  tm_dots(size=0.3)

```

We want to know. does this point pattern shown 

###Convert Daa to spatial Points Pattern
(combination of point data and the bounding window)

```{r}

spill_sp<-as(oil_sf, "Spatial")
spill_ppp<-as(spill_sp, "ppp")

#Want to create new spatial dataframe 
# ppp stands fr point pattern

tx_sp<-as(tex_border,"Spatial") 
tx_owin<-as(tx_sp, "owin")

all_ppp<-ppp(spill_ppp$x, spill_ppp$y, window = tx_owin)  

```

###A density plot 
```{r plot_bubbles}

plot(density(all_ppp, sigma = 0.1))

```

```{r }

oil_qt<-quadrat.test(all_ppp, nx=5,ny=5)
oil_qt
# The p value (significant) tells us that the data are not distributed, 
# NULL: data are csr 
# Would reject NULL hypothesis that the data are csr.

plot(all_ppp)
plot(oil_qt, add=TRUE, cex=0.4)
```
Looking at data, the observations do not look csr. 

**note the 14.5 in each quadrats**
PPP automatically 

###G-FUncion for Nearest Neighbor Analysis 
```{r}

r<- seq(0,1, by = 0.01)
oil_gfun <- envelope(all_ppp, fun=Gest, r=r, nsim=100)

ggplot(oil_gfun, aes(x=r, y=obs))+
  geom_line(color="black")+
  geom_line(aes(x=r, y=theo), color="red")

```

R has has a shirter proportion of point paired tend tohave nearestneighbor closer than we expect if it 
theo: modelled value for CSR. Comes from envelope. 

###Nearest neighbor using the L-function (ripley's K, standardized)
```{r}

r2<- seq(0,3, by=0.5)

oil_lfun<- envelope(all_ppp, fun = Lest, r=r2, nsim=20, global = TRUE)

ggplot(oil_lfun, aes(x=r2, y=obs))+
  geom_line(color="black")+
  geom_line(aes(x=r2, y=theo),color="blue")


```
